---
title: "My first R package"
author: 
 - Fabian
 - Heinz
date: '`r Sys.Date()`'
bibliography: my_references.bib
csl: applied-spectroscopy.csl
output: bookdown::pdf_document2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      fig.align = "center")
```

```{r}
library(mytestpkg)
```
# Numbers

## Multiplications

```{r mult}
b <- MultMean(c(10,12),2)
```

The result of our mean multiplication is `r b`.

I changed *something* very important.

## Quantile
Quantiles of random data are shown in Table \@ref(tab:tbl). The raw data is plotted in Figure \@ref(fig:plt). In a recent publication by [@costagliola2008impact] 
these numbers are not mentioned. But [@scott2016quantitative] are very interested in random data.

Ich will einen Konflikt provozieren!

```{r tbl}
x1 <- runif(1800,0,16) 
q1 <- quantile(x1)  
knitr::kable(q1, caption = 'Quantiles of random numbers.')
```

```{r plt, fig.cap="A plot of clr-transformed random numbers."}
library(mytestpkg)
hist(Sample100(x1))
```

# References
